---
title: "SujathaDist: An R Package for the Sujatha Distribution"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SujathaDist}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
library(SujathaDist)
set.seed(123)
```

# Introduction

The **SujathaDist** package provides functions for working with the Sujatha distribution, including

- Density function
- Distribution function
- Quantile function
- Random number generation
- Maximum likelihood estimation
- Goodness-of-fit statistics

# Density Function

```{r}
dsujatha(1, theta = 2)
```

# Distribution Function

```{r}
psujatha(1, theta = 2)
```

# Quantile Function

```{r}
qsujatha(0.5, theta = 2)
```

# Random Number Generation

```{r}
x <- rsujatha(100, theta = 2)
head(x)
```

# Parameter Estimation

```{r}
fit <- fitsujatha(x)

fit
```

# Summary

```{r}
summary(fit)
```

# Goodness-of-Fit

```{r}
gofsujatha(fit)
```

# Conclusion

The package provides a complete framework for inference on the Sujatha distribution.
